Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-09-26 vesicle_code/docs/permeableVes/main.tex
updating paper
worked on stenosis results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
Inspired by an experiment that measures the effects of cells on 
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
We consider the effect of stenosis on a semi-permeable vesicle. To allow
for large amounts of fluid flux through the membrane, we consider
geometry with a long constricted region. We start by considering a
vesicle initialized with reduced area $\nu = 0.65$, and we compare the
vesicle shape when $\beta = 0$ (impermeable) and $\beta = 10^{-3}$
(permeable). Figure~\ref{fig:stenosisShape} shows the vesicles' shape at
several locations along the constriction. The colors along the left
channel represent the tension and those along the right represent the
flux. In Figure~\ref{fig:stenosisTensionAndFux}, the tension at location
$x=20$ and the flux at location $x=30$ are plotted with respect to
arclength. The value of $\theta=0$ corresponds to the nose of the
vesicle.
\begin{figure}[htp]
  \ifTikz
%  \scalebox{0.5}{\input{figures/stenosisShapeTension01.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux02.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension03.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux04.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension05.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux06.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension07.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux08.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeTension09.tikz}}
  \scalebox{0.5}{\input{figures/stenosisShapeFlux10.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeTension11.tikz}}
%  \scalebox{0.5}{\input{figures/stenosisShapeFlux12.tikz}}
  \fi
  \caption{\label{fig:stenosisShape} An impermeable (dashed) and
  semi-permeable (solid) vesicle in a stenosed geometry (black).
  The vesicles' initial configuration are identical with reduced area
  $\nu = 0.65$. The color denotes the vesicles' tension (left) and flux
  (right). The semi-permeable vesicle deflates throughout the
  constriction (see Figure~\ref{fig:stenosisArea}) and develops higher
  curvature regions than its impermeable counterpart.}
\end{figure}

\begin{figure}[htp]
  \centering
  \ifTikz
  \scalebox{0.5}{\input{figures/stenosisTension09.tikz}}
  \scalebox{0.5}{\input{figures/stenosisFlux10.tikz}}
  \fi
  \caption{\label{fig:stenosisTensionAndFlux} The tension (left) and
  flux (right) of the semi-permeable (red) and impermeable (dashed blue)
  vesicles in Figure~\ref{fig:stenosisShape} at locations $x=20$ and
  $x=30$. The point $\theta=0$ corresponds to the right-most point of
  the vesicle.}
\end{figure}

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/stenosisArea.tikz}
  \fi
%  \includegraphics[width=0.8\linewidth]{figures/ellipseArea}
  \caption{\label{fig:stenosisArea} The area of a stenosed
  semi-permeable vesicle, with permeability rate $\beta=10^{-3}$. The
  $x$-axis is the $x$-coordinate of the center of mass of the vesicle.
  The vesicle loses fluid at a constant rate throughout the constriction
  that is between $\pm 60$. The semi-permeable vesicle loses 12.8\% of
  its fluid.}
\end{figure}

\begin{figure}[htp]
  \ifTikz
  \input{figures/stenosisBL.tikz}
  \fi
  \caption{\label{fig:stenosisBL} A stenosed semi-impermeable vesicle
  with reduced area 0.17. The initial reduced area is $0.20$. The bottom
  plot shows the velocity relative to the vesicle inside the square.
  The vesicle velocity in the square is nearly constant.}
\end{figure}

Inspired by an experiment that measures the effects of cells on 
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

@@

%\begin{figure}[htp]
%  \centering
%  \begin{tabular}{ccc}
%    \ifTikz
%    \scalebox{0.31}{\input{figures/stenosisTension1.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisTension3.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisTension5.tikz}} \\
%    \scalebox{0.31}{\input{figures/stenosisTension7.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisTension9.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisTension11.tikz}} 
%    \fi
%  \end{tabular}
%  \caption{\label{fig:stenosisTension} The tension of the impermeable
%  (red) and semi-permeable (dashed blue) vesicles in
%  Figure~\ref{fig:stenosisShape}. The point $\theta=0$ corresponds to
%  the right-most point of the vesicle.}
%\end{figure}
%
%\begin{figure}[htp]
%  \centering
%  \begin{tabular}{ccc}
%    \iftikz
%    \scalebox{0.31}{\input{figures/stenosisflux1.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisflux3.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisflux5.tikz}} \\
%    \scalebox{0.31}{\input{figures/stenosisflux7.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisflux9.tikz}} &
%    \scalebox{0.31}{\input{figures/stenosisflux11.tikz}} 
%    \fi
%  \end{tabular}
%  \caption{\label{fig:stenosisFlux} The flux (equivalent to pressure
%  jump) of the impermeable (red) and semi-permeable (dashed blue)
%  vesicles in Figure~\ref{fig:stenosisShape}. The point $\theta=0$
%  corresponds to the right-most point of the vesicle.}
%\end{figure}
